Indirect Conflicts: An Exploration and Discussion of Tools, Process, and Developer Insight

### 2013-08-13 iced-2013/paper.tex
ICED methodology draft except analysis.

Interview participants first answered a number of structured demographic items. Next, participants were 
asked to describe various software development processes they use or encounter in their current working
environment. These structured process questions were used for later analysis to provided context to
any answer for questions that involve indirect conflicts. They next were engaged in a
semi-structured round of questions pertaining to 12 categories of questions. Each of the categories was used as a
point of aggregation for later analysis as a way of answering the X research questions laid out in 
Section~\ref{sec:intro}. While each of the 12 question categories had a number of starter questions, interviews 
largely became discussions of developer experience and opinion as opposed to direct answers to any specific question.
In general, once the category was explained to the participant, little prompting was necessary as the participant
would jump right into an experience, or issue he or she had with the question or category. However, not all
participants had strong opinions or any experience on every category mentioned. For these participants, answers 
to the specific categories were not required or pressed upon. We attribute any non answer by a participant to
either lack of knowledge in their current project pertaining to the category or lack of experience in terms of
being apart of any one software project for extended periods of time. We account for these non answers
in our analysis as seen in Section~\ref{sec:rnd}. Interviews lasted 
from 15 minutes up to 75 minutes. The length of the interview largely depended on the amount of experience the
participant had in software development as they were able to give more experiences and more informed opinions.

@@

The created survey was based off of the 12 categorical hypotheses given by the round of interviews. The survey
was designed to test these hypotheses and to acquire a larger sample size of developers who may have similar
or different opinions from those already acquired from the interviews. The survey went through two rounds of
piloting. Each pilot round consisted of five participants, who were previously interviewed, completing the survey
with feedback given at the end. The previous interview participants were selected based on their domain knowledge
expertise with indirect conflicts in order to provide what we think would be amount to better feedback and resulting
in a more polished survey. The final survey consisted of 2 multiple choice, 3 level of agreement,
6 level of use, and 9 short answer questions. Each non demographic question was made optional as it was shown 
through the interviews that some questions require more experience from participants than may be provided.

>>>>

Interview participants first answered a number of structured demographic items. Next, participants were 
asked to describe various software development processes they use or encounter in their current working
environment. These structured process questions were used for later analysis to provided context to
any answer for questions that involve indirect conflicts. They next were engaged in a
semi-structured round of questions pertaining to 12 categories of questions.

\begin{itemize}
\item Software development tools for dependency tracking and awareness.
\item Software development process for preventing indirect conflicts.
\item Software artifact dependency levels and where conflicts can arise.
\item How developers find internal or external software dependencies.
\item Examples of indirect conflicts from real world experiences.
\item How indirect conflicts are detected and found.
\item How indirect conflict issues are solved or dealt with.
\item Developer opinion of preemptive measures to prevent indirect conflicts.
\item Developer opinion on what types of changes are worth a preemptive action.
\item Developer opinion on who is responsible for fixing or preventing indirect conflicts.
\end{itemize}

Each of the categories was used as a
point of aggregation for later analysis as a way of answering the X research questions laid out in 
Section~\ref{sec:intro}. While each of the 12 question categories had a number of starter questions, interviews 
largely became discussions of developer experience and opinion as opposed to direct answers to any specific question.
In general, once the category was explained to the participant, little prompting was necessary as the participant
would jump right into an experience, or issue he or she had with the question or category. However, not all
participants had strong opinions or any experience on every category mentioned. For these participants, answers 
to the specific categories were not required or pressed upon. We attribute any non answer by a participant to
either lack of knowledge in their current project pertaining to the category or lack of experience in terms of
being apart of any one software project for extended periods of time. We account for these non answers
in our analysis as seen in Section~\ref{sec:rnd}. Interviews lasted 
from 15 minutes up to 75 minutes. The length of the interview largely depended on the amount of experience the
participant had in software development as they were able to give more experiences and more informed opinions.

@@

The created survey was based off of the 12 categorical hypotheses given by the round of interviews. The survey
was designed to test these hypotheses and to acquire a larger sample size of developers who may have similar
or different opinions from those already acquired from the interviews. The survey went through two rounds of
piloting. Each pilot round consisted of five participants, who were previously interviewed, completing the survey
with feedback given at the end. The previous interview participants were selected based on their domain knowledge
expertise with indirect conflicts in order to provide what we think would be amount to better feedback and resulting
in a more polished survey. The final survey consisted of the following questions:
2 multiple choice questions for developer experience and demographic information; 3 level of agreement questions for an indication of
what types of environments indirect conflicts are more likely to occur;
6 level of use questions to indicate what types of software changed developers find trouble some with respect to
indirect conflicts; and 9 short answer questions for indication of when indirect conflicts occur, what types of
processes are used to prevent or react to indirect conflict, and to provide an outlet for general opinion
on the matter. Each non demographic question was made optional as it was shown 
through the interviews that some questions require more experience from participants than may be provided.
